CAKE: Classification \textit{avec} Kernel Embeddings \\ using Rademacher Complexity Bounds

### 2017-05-18 cake.tex
Revision for paper and appendix

% My Packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathbbol}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{vector}
\usepackage{cleveref}
\usepackage{bm}
\usepackage[dvipsnames]{xcolor}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{claim}[theorem]{Claim}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algorithmic}

%\usepackage{footnote}
%\makesavenoteenv{tabular}

\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newcommand{\note}[1]{{\color{orange} #1}}
\newcommand{\edit}[1]{{\color{forestgreen} #1}}

@@

\author{
	Kelvin Y.S. Hsu \\
	University of Sydney, Australia\\
	DATA61, CSIRO\\
	\texttt{Kelvin.Hsu@\{sydney.edu.au, data61.csiro.au\}} \\
	%% examples of more authors
	\And
	Richard Nock \\
	Australian National University, Australia\\
	University of Sydney, Australia\\
	DATA61, CSIRO\\
	\texttt{Richard.Nock@data61.csiro.au} \\
	\And
	Fabio T. Ramos \\
	University of Sydney, Australia\\
	DATA61, CSIRO\\
	\texttt{Fabio.Ramos@\{sydney.edu.au, data61.csiro.au\}} \\
	%% \texttt{email} \\
	%% \AND
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
	%% \And
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
	%% \And
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
}

\begin{document}
% \nipsfinalcopy is no longer used

@@

\begin{abstract}
	We propose learning-theoretic bounds for hyperparameter learning of conditional kernel embeddings in the probabilistic multiclass classification context. Kernel embeddings are nonparametric methods to represent probability distributions directly through observed data in a reproducing kernel Hilbert space (RKHS). This property forms the core of modern kernel methods, yet hyperparameter learning for kernel embeddings remains challenging, often relying on heuristics and domain expertise. We begin by developing the kernel embedding classifier (KEC), and prove its stochastic convergence for probabilistic inference. We then prove that its expected classification error can be bounded with high probability using Rademacher complexity based risk bounds. We use this bound to propose a scalable hyperparameter learning algorithm for conditional embeddings with batch stochastic gradient descent. We apply our learning algorithm to standard UCI datasets, as well as to learn feature representations of a convolutional neural network with improved accuracy, demonstrating the generality of this approach.
\end{abstract}

@@

	Kernel embeddings are principled methods to represent probability distributions in a nonparametric setting. By transforming distributions into mean embeddings within a reproducing kernel Hilbert space (RKHS), distributions can be represented directly from data without assuming a parametric structure \citep{song2013kernel}. Consequently, probabilistic inference can be carried out entirely within the RKHS nonparametrically, where difficult marginalisation integrals become simple linear algebra \citep{muandet2016kernel}. This very general and powerful technique is core to modern kernel methods, including support vector machines \citep{scholkopf2002learning}, kernel two-sample testing \citep{gretton2007kernel}, kernel Bayesian inference  \citep{fukumizu2013kernel}, nonparametric density estimation \citep{song2008tailoring, kanagawa2014recovering}, domain-invariant component analysis \citep{muandet2013domain}, dimensionality reduction \citep{fukumizu2004dimensionality}, feature discovery via hypothesis testing \citep{jitkrittum2016interpretable}, and filtering \citep{kanagawa2016filtering}. The problem of estimating the kernel mean in a reproducing kernel Hilbert space (RKHS) is thus central to kernel methods.

@@

	To construct a conditional embedding map $\mathcal{U}_{Y | X}$ corresponding to the distribution $\mathbb{P}_{Y | X}$, where $X : \Omega \to \mathcal{X}$ and $Y: \Omega \to \mathcal{Y}$ are measurable random variables, we choose a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ for the input space $\mathcal{X}$ and another kernel $l : \mathcal{Y} \times \mathcal{Y} \to \mathbb{R}$ for the output space $\mathcal{Y}$. These kernels $k$ and $l$ each describe how similarity is measured within each of their respective domains $\mathcal{X}$ and $\mathcal{Y}$, and are symmetric and positive definite such that they uniquely define the RKHS $\mathcal{H}_{k}$ and $\mathcal{H}_{l}$. We then define $\mathcal{U}_{Y | X} := C_{YX} C_{XX}^{-1}$ where $C_{YX} := \mathbb{E}[l(Y, \cdot) \otimes k(X, \cdot)]$ and $C_{XX} := \mathbb{E}[k(X, \cdot) \otimes k(X, \cdot)]$ \citep{song2009hilbert}. The conditional embedding map can be seen as an operator map from $\mathcal{H}_{k}$ to $\mathcal{H}_{l}$. In this sense, it sweeps out a family of conditional embeddings $\mu_{Y | X = x}$ in $\mathcal{H}_{l}$, each indexed by the input variable $x$, via the property $\mu_{Y | X = x} := \mathbb{E}[l(Y, \cdot) | X = x] = \mathcal{U}_{Y | X} k(x, \cdot)$.

@@

	In this section, we formulate a kernel embedding based probabilistic classifier by casting it into the conditional embedding framework. In the multiclass setting, the output label space is finite and discrete, taking values only in $\mathcal{Y} = \mathbb{N}_{m} := \{1, \dots, m\}$. Naturally, we first choose the Kronecker delta kernel $\delta : \mathbb{N}_{m} \times \mathbb{N}_{m} \to \{0, 1\}$ as the output kernel $l$, where labels that are the same has unit similarity and labels that are different have no similarity. That is, for all pairs of labels $y_{i}, y_{j} \in \mathcal{Y}$, $\delta(y_{i}, y_{j}) = 1$ only if $y_{i} = y_{j}$ and is $0$ otherwise. As $\delta$ is an integrally strictly positive definite kernel on $\mathbb{N}_{m}$, it is therefore characteristic \citep[Theorem 7]{sriperumbudur2010hilbert}. As such, by definition of characteristic kernels \citep{fukumizu2004dimensionality}, $\delta$ uniquely defines a RKHS  $\mathcal{H}_{\delta} = \overline{\mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}}$, which is the closure of the span of its kernel induced features \citep{xu2009refinement}. For $\mathcal{Y} = \mathbb{N}_{m}$, this means that any real-valued function $g : \mathbb{N}_{m} \to \mathbb{R}$ that is bounded on its discrete domain $\mathbb{N}_{m}$ is in the RKHS of $\delta$, because we can always write $g = \sum_{y = 1}^{m} g(y) \delta(y, \cdot) \in \mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}$. In particular, indicator functions on $\mathbb{N}_{m}$ are in the RKHS $\mathcal{H}_{\delta}$, since
	\begin{equation}
		\mathbb{1}_{c}(y) := \mathbb{1}_{\{c\}}(y) := \begin{cases}
		1 & \mathrm{if } \quad y \in \{c\} \\
		0 & \mathrm{otherwise}
		\end{cases} = \delta(c, y).
	\label{eq:indicator_function}
	\end{equation}
	That is, indicator functions $\mathbb{1}_{c} = \delta(c, \cdot)$, $c \in \mathbb{N}_{m}$ are simply the canonical kernel features of $\mathcal{H}_{\delta}$.

	While such properties does not necessarily hold for continuous domains in general, this convenient property in the case of a discrete domain $\mathcal{Y}$ with a Kronecker delta kernel $\delta$ is what allows consistent estimations of decision probabilities used in multiclass classification, which we turn to next.

	Let $p_{c}(x) := \mathbb{P}[Y = c | X = x]$ be the \textit{decision probability function} for class $c \in \mathbb{N}_{m}$, which is the probability of the class label $Y$ being $c$ when the example $X$ is $x$. We begin by writing this probability as an expectation of indicator functions,
	\begin{equation}
		p_{c}(x) := \mathbb{P}[Y = c | X = x] = \mathbb{P}[Y \in \{c\} | X = x] = \mathbb{E}[\mathbb{1}_{c}(Y) | X = x].
	\label{eq:decision_probability}
	\end{equation}	
	With $\mathbb{1}_{c} \in \mathcal{H}_{\delta}$, we let $g = \mathbb{1}_{c}$ in \eqref{eq:empirical_conditional_expectation} and $\bvec{1}_{c} := \{\mathbb{1}_{c}(y_{i})\}_{i = 1}^{n}$ to estimate the right hand side of \eqref{eq:decision_probability} by
	\begin{equation}
		\hat{p}_{c}(x) = f_{c}(x) := \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x).
	\label{eq:empirical_decision_probability}
	\end{equation}
	Therefore, the vector of empirical decision probability functions over the classes $c \in \mathbb{N}_{m}$ is
	\begin{equation}
		\hat{\bvec{p}}(x) = \bvec{f}(x) := \bvec{Y}^{T} (K + n \lambda I)^{-1} \bvec{k}(x) \in \mathbb{R}^{m},
	\label{eq:empirical_decision_probability_vector}
	\end{equation}
	where $\bvec{Y} := \begin{bmatrix} \bvec{1}_{1} & \bvec{1}_{2} & \cdots & \bvec{1}_{m} \end{bmatrix} \in \{0, 1\}^{n \times m}$ is simply the one hot encoded labels $\{y_{i}\}_{i = 1}^{n}$.

	We proceed to prove that the empirical decision probabilities \eqref{eq:empirical_decision_probability} converges to the true decision probabilities. In fact, the inference distribution \eqref{eq:empirical_decision_probability_vector} is equivalent to a conditional embedding.
	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
		\label{thm:probability_convergence_copy}
		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$. See appendix A for proof and other convergence results.
	\end{theorem}
	While decision probability estimates \eqref{eq:empirical_decision_probability} do not necessarily form a normalised distribution for finite $n$, \cref{thm:probability_convergence_copy} guarantees that they approach one with increasing sample sizes. When normalised distributions are required, distribution estimates \eqref{eq:empirical_decision_probability} can be clip-normalised,
	\begin{equation}
		\tilde{p}_{c}(x) := \frac{\max\{\hat{p}_{c}(x), 0\}}{\sum_{j = 1}^{m} \max\{\hat{p}_{j}(x), 0\}}.
	\label{eq:empirical_decision_probability_clip_normalised}
	\end{equation}
	Of course, classification $\hat{y}(x) = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x) = \argmax_{c \in \mathbb{N}_{m}} \tilde{p}_{c}(x)$ remains invariant.  \Cref{thm:probability_convergence_copy} also implies the reducing effect of clip-normalisation as with increasing sample sizes, where $\tilde{p}_{c}(x)$ approaches to both $\hat{p}_{c}(x)$ and $p_{c}(x)$.

@@

	Kernel embedding classifiers are equivalent to a conditional embedding with a discrete target space $\mathcal{Y}$. Hyperparameter learning for conditional embeddings is particularly difficult compared to joint embeddings, since the kernel $\{k_{\theta} : \theta \in \Theta\}$ is to be learned jointly with a regularisation parameter $\lambda \in \Lambda = \mathbb{R}_{+}$. While the conditional embedding map $\hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the operator $\mathcal{U}$ that minimises the regularised least squares loss $\frac{1}{n} \sum_{i = 1}^{n} \| \psi(y_{i}) - \mathcal{U} \phi(x_{i}) \|_{\mathcal{H}_{l}}^{2} + \lambda \| \mathcal{U} \|_{HS}$ in the RKHS \citep{song2013kernel}, minimising this loss directly over $\theta \in \Theta, \lambda \in \Lambda$ for $\mathcal{U} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X}$ would trivially result in an overfitted model with $\lambda \rightarrow 0$. This implies that the notion of model complexity is especially important, yet the standard solutions employ either cross validation or nested loops separating $\theta$ and $\lambda$, both of which are heuristics and subject to design choices.

@@

	We begin by defining a loss function as a measure for performance. For decision functions of the form $\bvec{f} : \mathcal{X} \to \mathcal{A} = \mathbb{R}^{m}$ whose entries are probability estimates, we employ the cross entropy loss,
	\begin{equation}
		\mathcal{L}_{\epsilon}(y, \bvec{f}(x)) := - \log{ [\bvec{y}^{T} \bvec{f}(x)]_{\epsilon}^{1} } = - \log{ [f_{y}(x)]_{\epsilon}^{1} },
	\label{eq:cross_entropy_loss_copy}
	\end{equation}
	to express classification risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$ for $\epsilon \in (0, 1)$. Under this loss, we prove that the expected risk for the kernel embedding classifier $\bvec{f} = \bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector} is bounded by the empirical risk and a Rademacher complexity bound $r(\theta, \lambda)$ with high probability. %We refer the reader to the supplementary material for detailed proof.

@@

	We refer the read to appendix B for proof. In order for the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} to be non-trivial, we focus on bounded kernels in the sense that $\alpha^{2}(\theta) := \sup_{x \in \mathcal{X}} k_{\theta}(x, x) < \infty$. Gaussian kernels $k_{\theta}(x, x') = \sigma_{f}^{2} \exp{( - \frac{1}{2}(x - x') \Sigma^{-1} (x - x') )}$ and similar stationary kernels (e.g. Mat\'{e}rn) with sensitivity and length scales $\theta = (\sigma_{f}, \Sigma)$, for example, have $\alpha(\theta) = \sigma_{f}$. Since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} is true with probability $1 - \beta$ when the random variables $X_{i}, Y_{i}$ are realised as the training observations $x_{i}, y_{i}$. We therefore employ this upper bound as the learning objective,
	\begin{equation}
		q(\theta, \lambda) := \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(y_{i}, \bvec{f}_{\theta, \lambda}(x_{i})) + 4 e \; r(\theta, \lambda).
	\label{eq:learning_objective}
	\end{equation}
	We employ gradient based optimisers such as Gradient descent or Adam \citep{kingma2014adam}. Since \cref{thm:expected_risk_bound_hyperparameter_learning_copy} holds for any $n \in \mathbb{N}_{+}$ and any set of data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ from $\mathbb{P}_{X Y}$, with the trade-off of relaxing bound tightness through $\sqrt{8 \log{(2 / \beta)} / n}$, the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} also holds with high probability for a subset of the training data. This enables scalable hyperparameter learning through batch stochastic gradient updates, where each gradient update stochastically improves a different upper bound of the generalisation risk. Because this bound holds with high probability over \textit{iid} samples, through randomly selecting a batch of training examples that comes from the same distribution, the resulting stochastic gradient will improve a strict upper bound with the same high probability. We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:kernel_embedding_classifier_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size. The Cholesky decomposition for the full training set requires $O(n^{3})$ time and is performed only once after learning instead of once every learning iteration, and can be avoided by using kernel herding \citep{chen2010super} or other kernel data reduction technique to select subsets to estimate the already learned embedding. All further inference steps take $O(n^{2})$ time for back substitution.

@@

	% , is general for any conditional embedding with discrete target space given any family of positive definite kernels $k_{\theta}$ over $\theta \in \Theta$ and $\lambda \in \Lambda$
	Our learning algorithm does not restrict the way the kernel $k_{\theta}$ is constructed from its parameters $\theta \in \Theta$. One particularly useful class of kernels are linear kernels with neural network features, in which the kernel $k(x, x') = \langle \varphi(x), \varphi(x') \rangle$ is constructed from neural networks $\varphi : \mathcal{X} \to \mathbb{R}^{p}$ explicitly. Neural networks are typically defined by weights and biases of its hidden layers, which collectively define the parameters of the constructed kernel, and are thus trainable under our learning algorithm. These kernels benefit in both scalability and expressibility. For large datasets, the $n \times n$ Cholesky decomposition required for full gradient updates in \cref{alg:kernel_embedding_classifier_training} can be transformed into a $p \times p$ decomposition by the Woodbury matrix inversion identity \citep{higham2002accuracy}. This allows scalability for $n >> p$ without using stochastic gradient updates so that the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} can be as tight as possible for a given $n$. Neural networks are by construction compositional, and thus latent representations of deeper networks undergo more transformations to generate a smaller and explicit collection of more expressive nonlinear features, leading to a deeper but narrower model architecture. This is in contrast to the potentially infinitely many implicit features from nonlinear kernels, which in turn define a shallower but wider model architecture. We direct the reader to appendix C for detailed discussion on the various kernel embedding classifier architectures.

@@

		83.7\% with only 500 data points

@@

\bibliographystyle{apalike}
\bibliography{kernel_embedding}

>>>>

% My Packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathbbol}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{vector}
\usepackage{cleveref}
\usepackage{bm}
\usepackage[dvipsnames]{xcolor}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{claim}[theorem]{Claim}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algorithmic}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}

@@

\author{
}

\begin{document}

@@

\begin{abstract}
	We propose learning-theoretic bounds for hyperparameter learning of conditional kernel embeddings in the probabilistic multiclass classification context. Kernel embeddings are nonparametric methods to represent probability distributions directly through observed data in a reproducing kernel Hilbert space (RKHS). This property forms the core of modern kernel methods, yet hyperparameter learning for kernel embeddings remains challenging, often relying on heuristics and domain expertise. We begin by developing the kernel embedding classifier (KEC), and prove its stochastic convergence for probabilistic inference. We then prove that its expected classification error can be bounded with high probability using Rademacher complexity bounds. We use this bound to propose a scalable hyperparameter learning algorithm for conditional embeddings with batch stochastic gradient descent. We apply our learning algorithm to standard UCI datasets, as well as to learn feature representations of a convolutional neural network with improved accuracy, demonstrating the generality of this approach.
\end{abstract}

@@

	Kernel embeddings are principled methods to represent probability distributions in a nonparametric setting. By transforming distributions into mean embeddings within a reproducing kernel Hilbert space (RKHS), distributions can be represented directly from data without assuming a parametric structure \citep{song2013kernel}. Consequently, nonparametric probabilistic inference can be carried out entirely within the RKHS, where difficult marginalisation integrals become simple linear algebra \citep{muandet2016kernel}. This very general and powerful technique is core to modern kernel methods, including support vector machines \citep{scholkopf2002learning}, kernel two-sample testing \citep{gretton2007kernel}, kernel Bayesian inference  \citep{fukumizu2013kernel}, nonparametric density estimation \citep{song2008tailoring, kanagawa2014recovering}, domain-invariant component analysis \citep{muandet2013domain}, dimensionality reduction \citep{fukumizu2004dimensionality}, feature discovery via hypothesis testing \citep{jitkrittum2016interpretable}, and filtering \citep{kanagawa2016filtering}. The problem of estimating the kernel mean in a reproducing kernel Hilbert space (RKHS) is thus central to kernel methods.

@@

	To construct a conditional embedding map $\mathcal{U}_{Y | X}$ corresponding to the distribution $\mathbb{P}_{Y | X}$, where $X : \Omega \to \mathcal{X}$ and $Y: \Omega \to \mathcal{Y}$ are measurable random variables, we choose a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ for the input space $\mathcal{X}$ and another kernel $l : \mathcal{Y} \times \mathcal{Y} \to \mathbb{R}$ for the output space $\mathcal{Y}$. These kernels $k$ and $l$ each describe how similarity is measured within their respective domains $\mathcal{X}$ and $\mathcal{Y}$, and are symmetric and positive definite such that they uniquely define the RKHS $\mathcal{H}_{k}$ and $\mathcal{H}_{l}$. We then define $\mathcal{U}_{Y | X} := C_{YX} C_{XX}^{-1}$ where $C_{YX} := \mathbb{E}[l(Y, \cdot) \otimes k(X, \cdot)]$ and $C_{XX} := \mathbb{E}[k(X, \cdot) \otimes k(X, \cdot)]$ \citep{song2009hilbert}. The conditional embedding map can be seen as an operator map from $\mathcal{H}_{k}$ to $\mathcal{H}_{l}$. In this sense, it sweeps out a family of conditional embeddings $\mu_{Y | X = x}$ in $\mathcal{H}_{l}$, each indexed by the input variable $x$, via the property $\mu_{Y | X = x} := \mathbb{E}[l(Y, \cdot) | X = x] = \mathcal{U}_{Y | X} k(x, \cdot)$.

@@

	In this section, we formulate a kernel embedding based probabilistic classifier by casting it into the conditional embedding framework. In the multiclass setting, the output label space is finite and discrete, taking values only in $\mathcal{Y} = \mathbb{N}_{m} := \{1, \dots, m\}$. Naturally, we first choose the Kronecker delta kernel $\delta : \mathbb{N}_{m} \times \mathbb{N}_{m} \to \{0, 1\}$ as the output kernel $l$, where labels that are the same has unit similarity and labels that are different have no similarity. That is, for all pairs of labels $y_{i}, y_{j} \in \mathcal{Y}$, $\delta(y_{i}, y_{j}) = 1$ only if $y_{i} = y_{j}$ and is $0$ otherwise. As $\delta$ is an integrally strictly positive definite kernel on $\mathbb{N}_{m}$, it is therefore characteristic \citep[Theorem 7]{sriperumbudur2010hilbert}. As such, by definition of characteristic kernels \citep{fukumizu2004dimensionality}, $\delta$ uniquely defines a RKHS  $\mathcal{H}_{\delta} = \overline{\mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}}$, which is the closure of the span of its kernel induced features \citep{xu2009refinement}. For $\mathcal{Y} = \mathbb{N}_{m}$, this means that any real-valued function $g : \mathbb{N}_{m} \to \mathbb{R}$ that is bounded on its discrete domain $\mathbb{N}_{m}$ is in the RKHS of $\delta$, because we can always write $g = \sum_{y = 1}^{m} g(y) \delta(y, \cdot) \in \mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}$. In particular, indicator functions on $\mathbb{N}_{m}$ are in the RKHS $\mathcal{H}_{\delta}$, since
	\begin{equation}
		\mathbb{1}_{c}(y) := \mathbb{1}_{\{c\}}(y) := \begin{cases}
		1 & \mathrm{if } \quad y \in \{c\} \\
		0 & \mathrm{otherwise}
		\end{cases} = \delta(c, y).
	\label{eq:indicator_function}
	\end{equation}
	That is, indicator functions $\mathbb{1}_{c} = \delta(c, \cdot)$, $c \in \mathbb{N}_{m}$, are simply the canonical kernel features of $\mathcal{H}_{\delta}$. Such properties do not necessarily hold for continuous domains in general. This convenient property in the case of a discrete domain $\mathcal{Y}$ with a Kronecker delta kernel $\delta$ is what allows consistent estimations of decision probabilities used in multiclass classification, which we turn to next.

	Let $p_{c}(x) := \mathbb{P}[Y = c | X = x]$ be the \textit{decision probability function} for class $c \in \mathbb{N}_{m}$, which is the probability of the class label $Y$ being $c$ when the example $X$ is $x$. We begin by writing this probability as an expectation of indicator functions,
	\begin{equation}
		p_{c}(x) := \mathbb{P}[Y = c | X = x] = \mathbb{P}[Y \in \{c\} | X = x] = \mathbb{E}[\mathbb{1}_{c}(Y) | X = x].
	\label{eq:decision_probability}
	\end{equation}	
	With $\mathbb{1}_{c} \in \mathcal{H}_{\delta}$, we let $g = \mathbb{1}_{c}$ in \eqref{eq:empirical_conditional_expectation} and $\bvec{1}_{c} := \{\mathbb{1}_{c}(y_{i})\}_{i = 1}^{n}$ to estimate the right hand side of \eqref{eq:decision_probability} by
	\begin{equation}
		\hat{p}_{c}(x) = f_{c}(x) := \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x).
	\label{eq:empirical_decision_probability}
	\end{equation}
	Therefore, the vector of empirical decision probability functions over the classes $c \in \mathbb{N}_{m}$ is
	\begin{equation}
		\hat{\bvec{p}}(x) = \bvec{f}(x) := \bvec{Y}^{T} (K + n \lambda I)^{-1} \bvec{k}(x) \in \mathbb{R}^{m},
	\label{eq:empirical_decision_probability_vector}
	\end{equation}
	where $\bvec{Y} := \begin{bmatrix} \bvec{1}_{1} & \bvec{1}_{2} & \cdots & \bvec{1}_{m} \end{bmatrix} \in \{0, 1\}^{n \times m}$ is simply the one hot encoded labels $\{y_{i}\}_{i = 1}^{n}$. The kernel embedding classifier is thus the multi-valued decision function $\bvec{f}(x)$ \eqref{eq:empirical_decision_probability_vector}. We proceed to prove that empirical decision probabilities \eqref{eq:empirical_decision_probability} converge to the true decision probabilities. In fact, the inference distribution \eqref{eq:empirical_decision_probability_vector} is equivalent to the empirical conditional embedding.
	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
		\label{thm:probability_convergence_copy}
		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$. See appendix A for proof and other convergence results.
	\end{theorem}
	While decision probability estimates \eqref{eq:empirical_decision_probability} do not necessarily form a normalised distribution for finite $n$, \cref{thm:probability_convergence_copy} guarantees that they approach one with increasing sample size. When normalised distributions are required, distribution estimates \eqref{eq:empirical_decision_probability} can be clip-normalised,
	\begin{equation}
		\tilde{p}_{c}(x) := \frac{\max\{\hat{p}_{c}(x), 0\}}{\sum_{j = 1}^{m} \max\{\hat{p}_{j}(x), 0\}}.
	\label{eq:empirical_decision_probability_clip_normalised}
	\end{equation}
	Of course, classification $\hat{y}(x) = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x) = \argmax_{c \in \mathbb{N}_{m}} \tilde{p}_{c}(x)$ remains invariant.  \Cref{thm:probability_convergence_copy} also implies the reducing effect of clip-normalisation as with increasing sample sizes, where $\tilde{p}_{c}(x)$ approaches to both $\hat{p}_{c}(x)$ and $p_{c}(x)$.

@@

	Kernel embedding classifiers \eqref{eq:empirical_decision_probability} are equivalent to a conditional embedding with a discrete target space $\mathcal{Y}$. Hyperparameter learning for conditional embeddings is particularly difficult compared to joint embeddings, since the kernel $k_{\theta}$ with parameters $\theta \in \Theta$ is to be learned jointly with a regularisation parameter $\lambda \in \Lambda = \mathbb{R}_{+}$. While the conditional embedding map $\hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the operator $\mathcal{U}$ that minimises the regularised least squares loss $\frac{1}{n} \sum_{i = 1}^{n} \| \psi(y_{i}) - \mathcal{U} \phi(x_{i}) \|_{\mathcal{H}_{l}}^{2} + \lambda \| \mathcal{U} \|_{HS}$ in the RKHS \citep{song2013kernel}, minimising this loss directly over $\theta \in \Theta, \lambda \in \Lambda$ for $\mathcal{U} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X}$ would trivially result in an overfitted model with $\lambda \rightarrow 0$. This implies that the notion of model complexity is especially important, yet the standard solutions employ either cross validation or nested loops separating $\theta$ and $\lambda$, both of which are heuristics and subject to design choices.

@@

	We begin by defining a loss function as a measure for performance. For decision functions of the form $\bvec{f} : \mathcal{X} \to \mathcal{A} = \mathbb{R}^{m}$ whose entries are probability estimates, we employ the cross entropy loss,
	\begin{equation}
		\mathcal{L}_{\epsilon}(y, \bvec{f}(x)) := - \log{ [\bvec{y}^{T} \bvec{f}(x)]_{\epsilon}^{1} } = - \log{ [f_{y}(x)]_{\epsilon}^{1} },
	\label{eq:cross_entropy_loss_copy}
	\end{equation}
	to express classification risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$ for $\epsilon \in (0, 1)$. Under this loss, we prove that the expected risk for the kernel embedding classifier $\bvec{f} = \bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector} is bounded by the empirical risk and a Rademacher complexity bound $r(\theta, \lambda)$ with high probability.

@@

	We refer the reader to appendix B for proof. In order for the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} to be non-trivial, we focus on bounded kernels in the sense that $\alpha^{2}(\theta) := \sup_{x \in \mathcal{X}} k_{\theta}(x, x) < \infty$. Gaussian kernels $k_{\theta}(x, x') = \sigma_{f}^{2} \exp{( - \frac{1}{2}(x - x') \Sigma^{-1} (x - x') )}$ and similar stationary kernels (e.g. Mat\'{e}rn) with sensitivity and length scales $\theta = (\sigma_{f}, \Sigma)$, for example, have $\alpha(\theta) = \sigma_{f}$. Since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} is true with probability $1 - \beta$ when the random variables $X_{i}, Y_{i}$ are realised as the training observations $x_{i}, y_{i}$. We therefore employ this upper bound as the learning objective,
	\begin{equation}
		q(\theta, \lambda) := \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(y_{i}, \bvec{f}_{\theta, \lambda}(x_{i})) + 4 e \; r(\theta, \lambda).
	\label{eq:learning_objective}
	\end{equation}
	We employ gradient based optimisers such as Gradient descent or Adam \citep{kingma2014adam}. Since \cref{thm:expected_risk_bound_hyperparameter_learning_copy} holds for any $n \in \mathbb{N}_{+}$ and any set of data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ from $\mathbb{P}_{X Y}$, with the trade-off of relaxing bound tightness through $\sqrt{8 \log{(2 / \beta)} / n}$, the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} also holds with high probability for a subset of the training data. This enables scalable hyperparameter learning through batch stochastic gradient updates, where each gradient update stochastically improves a different upper bound of the generalisation risk. Because this bound holds with high probability over \textit{iid} samples, through randomly selecting a batch of training examples that comes from the same distribution, the resulting stochastic gradient will improve a strict upper bound with the same high probability. We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:kernel_embedding_classifier_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size. The Cholesky decomposition for the full training set requires $O(n^{3})$ time and is performed only once after learning instead of once every learning iteration, and can be avoided by using kernel herding \citep{chen2010super} or other kernel data reduction technique to select subsets to estimate the already learned embedding. All further inference steps take $O(n^{2})$ time for back substitution.

@@

	Our learning algorithm does not restrict the way the kernel $k_{\theta}$ is constructed from its parameters $\theta \in \Theta$. One particularly useful class of kernels are those with explicit neural network features, in which the kernel $k(x, x') = \langle \varphi(x), \varphi(x') \rangle$ is constructed from neural networks $\varphi : \mathcal{X} \to \mathbb{R}^{p}$ explicitly. Neural networks are typically defined by weights and biases of its hidden layers, which collectively define the parameters of the constructed kernel, and are thus trainable under our learning algorithm. These kernels benefit in both scalability and expressibility. For large datasets, the $n \times n$ Cholesky decomposition required for full gradient updates in \cref{alg:kernel_embedding_classifier_training} can be transformed into a $p \times p$ decomposition by the Woodbury matrix inversion identity \citep{higham2002accuracy}. This allows scalability for $n >> p$ without using stochastic gradient updates so that the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} can be as tight as possible for a given $n$. Neural networks are by construction compositional, and thus latent representations of deeper networks undergo more transformations to generate a smaller and explicit collection of more expressive nonlinear features, leading to a deeper but narrower model architecture. This is in contrast to the potentially infinitely many implicit features from nonlinear kernels, which in turn define a shallower but wider model architecture. We direct the reader to appendix C for detailed discussion on the various kernel embedding classifier architectures.

@@

%		83.7\% with only 500 data points

@@

\newpage
\bibliographystyle{apalike}
\bibliography{kernel_embedding}
